Pheromone processing in \emph{Drosophila}

### 2015-04-01 Paper.tex

\begin{tabular*}{0.85\paperwidth}{@{\extracolsep{\fill}}|>{\raggedright}p{0.07\paperwidth}|>{\centering}p{0.04\paperwidth}|>{\centering}p{0.06\paperwidth}|>{\centering}p{0.06\paperwidth}|>{\centering}p{0.03\paperwidth}|>{\centering}p{0.12\paperwidth}|>{\centering}p{0.2\paperwidth}|>{\centering}p{0.07\paperwidth}|}
\hline 
\textbf{Pheromone} & \textbf{Range} & \textbf{emitter → detector} & \textbf{Receptor} & \textbf{PN} & \textbf{Behavior} & \textbf{Comments} & \textbf{References}\tabularnewline
\hline 
\hline 
\multirow{5}{0.07\paperwidth}{cVA} & \multirow{5}{0.04\paperwidth}{volatile \& contact} & M → M & \textcolor{blue}{Or67d} & \textcolor{blue}{DA1} & aggression & suppressed by chronic cVA via Or65a & \citep{Wang:2010kl,Ejima:2007bs,Liu:2011dq}\tabularnewline
\cline{3-8} 
 &  & F → M & \textcolor{blue}{Or67d} & \textcolor{blue}{DA1} & male repulsion & transferred to female by prior mating & \citep{Kurtovic:2007fu}\tabularnewline
\cline{3-8} 
 &  & M → F & \textcolor{blue}{Or67d} & \textcolor{blue}{DA1} & female receptivity & suppressed by chronic cVA via Or65a & \citep{Kurtovic:2007fu,Lebreton:2014cr}\tabularnewline
\cline{3-8} 
 &  & M/F → M/F & Or65a (?) & DL3 (?) & aggregation\textsuperscript{4} &  & \citep{Bartelt:1985bh}\tabularnewline
\cline{3-8} 
 &  & M → M & \textcolor{blue}{\emph{ppk23}}\textcolor{blue}{/}\textcolor{blue}{\emph{ppk29}}\textsuperscript{1} & n/a & male-male repulsion & \emph{ppk} channels pheromone receptors ? & \citep{Thistle:2012fu}\tabularnewline
\hline 
\multirow{3}{0.07\paperwidth}{7-T} & \multirow{3}{0.04\paperwidth}{contact} & M → F & Gr32a & n/a & female receptivity & increases female receptivity & \citep{Grillet:2006tg}\tabularnewline
\cline{3-8} 
 &  & M → M & Gr32a (Gr66a) & n/a & male-male / interspecies repulsion &  & \citep{Fan:2013fv,Lacaille:2007ij}\tabularnewline
\cline{3-8} 
 &  & M → M & \textcolor{blue}{\emph{ppk23}}\textcolor{blue}{/}\textcolor{blue}{\emph{ppk29}}\textsuperscript{1} & n/a & male-male repulsion & \emph{ppk} channels pheromone receptors ? & \citep{Toda:2012ff,Starostina:2012mi,Liu:2012ys,Thistle:2012fu}\tabularnewline
\hline 
7-P & contact & M → F & ? & n/a & female receptivity (?) & male-enriched & \citep{Ferveur:2005ly,Yew:2009fv}\tabularnewline
\hline 
7,11-HD (7,11-ND)\textsuperscript{3} & contact & F → M & \textcolor{blue}{\emph{ppk23}}\textcolor{blue}{/}\textcolor{blue}{\emph{ppk29}}\textcolor{blue}{/}

>>>>

\begin{tabular*}{0.85\paperwidth}{@{\extracolsep{\fill}}|>{\raggedright}p{0.07\paperwidth}|>{\centering}p{0.04\paperwidth}|>{\centering}p{0.06\paperwidth}|>{\centering}p{0.06\paperwidth}|>{\centering}p{0.03\paperwidth}|>{\centering}p{0.12\paperwidth}|>{\centering}p{0.2\paperwidth}|>{\centering}p{0.07\paperwidth}|}
\hline 
\textbf{Pheromone} & \textbf{Range} & \textbf{emitter → detector} & \textbf{Receptor} & \textbf{PN} & \textbf{Behavior} & \textbf{Comments} & \textbf{Refs}\tabularnewline
\hline 
\hline 
\multirow{5}{0.07\paperwidth}{cVA} & \multirow{5}{0.04\paperwidth}{volatile \& contact} & M → M & \textcolor{blue}{Or67d} & \textcolor{blue}{DA1} & aggression & suppressed by chronic cVA via Or65a & \citep{Wang:2010kl,Ejima:2007bs,Liu:2011dq}\tabularnewline
\cline{3-8} 
 &  & F → M & \textcolor{blue}{Or67d} & \textcolor{blue}{DA1} & male repulsion & transferred to female by prior mating & \citep{Kurtovic:2007fu}\tabularnewline
\cline{3-8} 
 &  & M → F & \textcolor{blue}{Or67d} & \textcolor{blue}{DA1} & female receptivity & suppressed by chronic cVA via Or65a & \citep{Kurtovic:2007fu,Lebreton:2014cr}\tabularnewline
\cline{3-8} 
 &  & M/F → M/F & Or65a (?) & DL3 (?) & aggregation\textsuperscript{4} & \  & \citep{Bartelt:1985bh}\tabularnewline
\cline{3-8} 
 &  & M → M & \textcolor{blue}{\emph{ppk23}}\textcolor{blue}{/}\textcolor{blue}{\emph{ppk29}}\textsuperscript{1} & n/a & male-male repulsion & \emph{ppk} channels pheromone receptors ? & \citep{Thistle:2012fu}\tabularnewline
\hline 
\multirow{3}{0.07\paperwidth}{7-T} & \multirow{3}{0.04\paperwidth}{contact} & M → F & Gr32a & n/a & female receptivity & increases female receptivity & \citep{Grillet:2006tg}\tabularnewline
\cline{3-8} 
 &  & M → M & Gr32a (Gr66a) & n/a & male-male / interspecies repulsion & \  & \citep{Fan:2013fv,Lacaille:2007ij}\tabularnewline
\cline{3-8} 
 &  & M → M & \textcolor{blue}{\emph{ppk23}}\textcolor{blue}{/}\textcolor{blue}{\emph{ppk29}}\textsuperscript{1} & n/a & male-male repulsion & \emph{ppk} channels pheromone receptors ? & \citep{Toda:2012ff,Starostina:2012mi,Liu:2012ys,Thistle:2012fu}\tabularnewline
\hline 
7-P & contact & M → F & ? & n/a & female receptivity (?) & male-enriched & \citep{Ferveur:2005ly,Yew:2009fv}\tabularnewline
\hline 
7,11-HD (7,11-ND)\textsuperscript{3} & contact & F → M & \textcolor{blue}{\emph{ppk23}}\textcolor{blue}{/}\textcolor{blue}{\emph{ppk29}}\textcolor{blue}{/}
